Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-03-28 draft.tex
replace table3,4,5 with mpi rank avg. communication time

\begin{table}[ht]
\begin{center}
\caption{Time spent on communication by Workload I when dragonfly network equipped with 6 different placement and routing configurations.} 
\label{tab:wkld-commtime}
%\centering % Centers the table on the page, comment out to left-justify
\begin{tabular}{l c c c c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{6}{c}{Placement and Routing Configurations} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
\cmidrule(l){2-7}
	 & CM & CA & CPA & RM & RA & RPA \\ % Column names row
\midrule % In-table horizontal line
Time(ms)  &  1870 & 1250 & 1248 & 860 & 835 &830\\ % Content row 1

@@

The communication time spent by Workload \Rmnum{1} under different placement and routing configurations shown in Table \ref{tab:wkld-commtime}. The contiguous placement coupled with minimal routing (CM) results in highest communication time. When contiguous placement coupled with progressive adaptive and adaptive routing (CA, CPA), Workload \Rmnum{1} spends  comparable amount of time to complete communication. The random placement policy performs comparably with all routing policies and outperforms all contiguous placement configurations.

@@

So far we know that the reason for AMG being the only victim from random placement \& adaptive routing is due to its relatively small amount of data transfer, that make it the least communication-intensive application in the workload.

@@

\emph{Network performance will be significantly improved when random placement and adaptive routing are in use.} Random placement can uniformly distribute MPI ranks of application over the network, and adaptive routing can redirect the traffic from congested routers to other less busy routers. Therefore, the network could reach load-balance and hot-spots.

\emph{The performance of less communication-intensive jobs in workload will suffer degradation when network is configured with random placement and adaptive routing.}\NOTE{footnote} AMG in Workload \Rmnum{1} are ``bullied" by their concurrently running communication-intensive peers, MultiGrid and CrystalRouter. AMG shares routers and groups with MultiGrid and CrystalRouter when random placement is in use. The traffic from MultiGrid and CrystalRouter will be redirected to the routers that serving AMG, slow down AMG's communication.

@@

\TODO{make this paragraph into footnote} We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.

@@

\begin{table}[ht]
\begin{center}
\caption{Time spent on communication (MilliSecond) by Workload II when 6 different placement\&routing configuration in use.} 
\label{tab:syn-wkld-commtime}
%\centering % Centers the table on the page, comment out to left-justify
\begin{tabular}{l c c c c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{6}{c}{Placement\&Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
\cmidrule(l){2-7}
	 & CM & CA & CPA & RM & RA & RPA \\ % Column names row
\midrule % In-table horizontal line
Runtime  &  6123 & 3231 & 3725 & 2544 & 3701 & 3228 \\ % Content row 1

@@

The communication time spent by parallel workload \Rmnum{2} under different placement \& routing configurations shown in Table \ref{tab:syn-wkld-commtime}. As the overall traffic increased in the workload(due to sAMG), the time spent on communication under each configuration also increases. But the performance of each configuration still keep the same trend as parallel workload \Rmnum{1}. The contiguous placement coupled with minimal routing results in highest communication time. The random placement coupled with minimal routing is the most efficient. Progressive adaptive routing is better than adaptive routing when random placement is in use. And they have comparable results when coupled contiguous placement.

Figure \ref{fig:synwkld-network-traffic-stime} show the network status when Workload \Rmnum{2} running under different placement \& routing configurations. Contiguous placement coupled with minimal routing result in most traffic go through certain local and global channel, thus the longest  communication time for terminal link, local and global channel. When coupled with (progressive) adaptive routing, the local congestion can get alleviated in contiguous placement. The random placement reach the comparable performance with any routing schemes in terms of both traffic and busy time. They are better than contiguous \& minimal configuration, but not too much improvement against contiguous\&(progressive) adaptive configuration.

@@

% explain the network status of sAMG, MG and CR
We look into the network level to scrutinize the traffic go through the routers belongs to each application. 
Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers that belongs to sAMG when different placement \& routing configuration in use. The traffic is skyrocketing in both local and global channels when contiguous placement coupled with minimal routing. The contiguous placement make all the MPI ranks of sAMG reside on a set of nodes in the groups that adjacent to each other and minimal routing confines the traffic in those groups, results in severe local congestion. When adaptive routing is used, the local congestion will be alleviated in both local and global channels, as some traffic will be redirected to other part of the network. Random placement scheme can further reduce the traffic burden on local and global channels by assigning each MPI rank of sAMG with randomly select nodes, thus uniformly distribute sAMG traffic over the network.

@@

>>>>

\begin{table}[ht]
\begin{center}
\caption{Average time spent on communication by all MPI ranks when Workload I is running on dragonfly network under 6 different placement and routing configurations.} 
\label{tab:wkld-commtime}
%\centering % Centers the table on the page, comment out to left-justify
\begin{tabular}{l c c c c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{6}{c}{Placement and Routing Configurations} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
\cmidrule(l){2-7}
	      & CM & CA & CPA & RM & RA & RPA \\ % Column names row
\midrule % In-table horizontal line
Time(ms)  & 476  & 300  & 301  & 255  & 265  & 264  \\ % Content row 1

@@

The average communication time spent by all MPI ranks when Workload \Rmnum{1} is running under different placement and routing configurations shown in Table \ref{tab:wkld-commtime}. The contiguous placement coupled with minimal routing (CM) results in highest communication time. When contiguous placement coupled with progressive adaptive and adaptive routing (CA, CPA), Workload \Rmnum{1} spends  comparable amount of time to complete communication. The random placement policy performs comparably with all routing policies and outperforms all contiguous placement configurations.

@@

So far we know that the reason for AMG being the only victim from random placement and adaptive routing is due to its relatively small amount of data transfer, that make it the least communication-intensive application in the workload.

@@

\emph{Network performance will be significantly improved when random placement and adaptive routing are in use.} Random placement can uniformly distribute MPI ranks of application over the network, and adaptive routing can redirect the traffic from congested routers to other less busy routers. Therefore, the network could reach the status of load-balanced and hot-spots free.

\emph{The performance of less communication-intensive jobs in workload will suffer degradation when network is configured with random placement and adaptive routing.} AMG in Workload \Rmnum{1} are ``bullied" by their concurrently running communication-intensive peers, MultiGrid and CrystalRouter. AMG shares routers and groups with MultiGrid and CrystalRouter when random placement is in use. The traffic from MultiGrid and CrystalRouter will be redirected to the routers that serving AMG, slow down AMG's communication. \footnote{We have tried three different congestion sensing schemes that used in adaptive routing\cite{won-prog-adaptive}, although there are some variations between the results, none of the congestion sensing scheme can prevent the ``bully" from happening.}

@@

@@

\begin{table}[ht]
\begin{center}
\caption{Average time spent on communication by all MPI ranks when Workload II is running on dragonfly network under 6 different placement and routing configurations.} 
\label{tab:syn-wkld-commtime}
%\centering % Centers the table on the page, comment out to left-justify
\begin{tabular}{l c c c c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{6}{c}{Placement and Routing Configuration} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
\cmidrule(l){2-7}
	      & CM & CA & CPA & RM & RA & RPA \\ % Column names row
\midrule % In-table horizontal line
Time(ms)  & 3360 & 2204 & 2335 & 1791 & 2367 & 1965 \\ % Content row 1

@@

The average communication time spent by all MPI ranks when Workload \Rmnum{2} running under different placement and routing configurations shown in Table \ref{tab:syn-wkld-commtime}. As the overall traffic increased in the workload(due to sAMG), the time spent on communication under each configuration also increases. But the performance of each configuration still keep the similar trend as parallel Workload \Rmnum{1}. The contiguous placement coupled with minimal routing results in highest communication time. The random placement coupled with minimal routing is the most efficient. Progressive adaptive routing is better than adaptive routing when random placement is in use. And they have comparable results when coupled contiguous placement.

Figure \ref{fig:synwkld-network-traffic-stime} show the network status when Workload \Rmnum{2} running under different placement and routing configurations. Contiguous placement coupled with minimal routing result in most traffic go through certain local and global channel, thus the longest  communication time for terminal link, local and global channel. When coupled with (progressive) adaptive routing, the local congestion can get alleviated in contiguous placement. The random placement reach the comparable performance with any routing schemes in terms of both traffic and busy time. They are better than contiguous and minimal configuration, but not too much improvement against contiguous and (progressive) adaptive configuration.

@@

% explain the network status of sAMG, MG and CR
We look into the network level to scrutinize the traffic go through the routers belongs to each application. 
Figure \ref{fig:syn-samg-lc-traffic}, \ref{fig:syn-samg-gc-traffic} shows the traffic go through the local and global channels of the routers that belongs to sAMG when different placement and routing configuration in use. The traffic is skyrocketing in both local and global channels when contiguous placement coupled with minimal routing. The contiguous placement make all the MPI ranks of sAMG reside on a set of nodes in the groups that adjacent to each other and minimal routing confines the traffic in those groups, results in severe local congestion. When adaptive routing is used, the local congestion will be alleviated in both local and global channels, as some traffic will be redirected to other part of the network. Random placement scheme can further reduce the traffic burden on local and global channels by assigning each MPI rank of sAMG with randomly select nodes, thus uniformly distribute sAMG traffic over the network.

@@

\begin{table}[ht]
\begin{center}
\caption{Average time spent on communication by all MPI ranks when Workload I, II are running on dragonfly network under hybrid placement and random placement policies.} 
\label{tab: hyb-placement-wkld-commtime}
%\centering % Centers the table on the page, comment out to left-justify
\begin{tabular}{l c c c c c c }
\toprule % Top horizontal line
\toprule
&\multicolumn{6}{c}{Placement and Routing Configurations} \\ % Amalgamating several columns into one cell is done using the \multicolumn command as seen on this line
\cmidrule(l){2-7}
	      & HM & HA & HPA & RM & RA & RPA \\ % Column names row
\midrule % In-table horizontal line
Workload I  &273 &255 &255 &255 &265 &264  \\ % Content row 1
\midrule
Workload II &1747 &1991 &1991 &1791 &2367 &1965 \\
\midrule % In-table horizontal line
\bottomrule % Bottom horizontal line
\end{tabular}
\end{center}
\end{table}
